% This file is part of Mūlārthabodhinī XeLaTeX Source Code
% Mūlārthabodhinī XeLaTeX Source Code is free software: you can redistribute it and/or modify it under the terms of the GNU General Public License as published by the Free Software Foundation, either version 3 of the License, or (at your option) any later version.
% Mūlārthabodhinī XeLaTeX Source Code is distributed in the hope that it will be useful, but WITHOUT ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the GNU General Public License for more details.
% You should have received a copy of the GNU General Public License along with Mūlārthabodhinī XeLaTeX Source Code. If not, see <https://www.gnu.org/licenses/>.
अ.को. & अमरकोष\\[1mm]
अ.सं.प. & अगस्त्य संहिता परिशिष्ट\\[1mm]
ई.उ.शा.पा. & ईशावास्य उपनिषद् शान्तिपाठ\\[1mm]
क. & कवितावली\\[1mm]
कृ.क.अ. & कृष्णकर्णामृत\\[1mm]
ग.सं. & गर्गसंहिता\\[1mm]
गी. & गीतावली\\[1mm]
गी.गो. & गीतगोविन्द\\[1mm]
च.प.स्तो. & चर्पटपञ्जरिकास्तोत्र\\[1mm]
ज.अ. & जगन्नाथाष्टक\\[1mm]
तु.स.स. & तुलसी सतसई\\[1mm]
दु.स.श. & दुर्गासप्तशती\\[1mm]
दो. & दोहावली\\[1mm]
नी.श. & नीतिशतक\\[1mm]
पा.गी. & पाण्डव गीता\\[1mm]
पा.सू. & पाणिनि सूत्र (अष्टाध्यायी)\\[1mm]
ब.रा. & बरवै रामायण \\[1mm]
भ.गी. & श्रीमद्भगवद्गीता\\[1mm]
भ.पु.प्रति.प. & भविष्यपुराण प्रतिसर्गपर्व\\[1mm]
भ.मा. & भक्तमाल\\[1mm]
भ.र.बो. & भक्तिरसबोधिनी (प्रियादासजीकृत भक्तमालटीका)\\[1mm]
भ.र.सि. & भक्तिरसामृतसिन्धु\\[1mm]
भा.पु. & श्रीमद्भागवतपुराण\\[1mm]
भा.पु.श्री.टी. & श्रीमद्भागवतपुराण श्रीधरटीका \\[1mm]
भा.पु.श्री.टी.म. & श्रीमद्भागवतपुराण श्रीधरटीका मङ्गलाचरण \\[1mm]
म.स्मृ. & मनुस्मृति\\[1mm]
मा. & श्रीरामचरितमानस\\[1mm]
मा.पु. & मार्कण्डेय पुराण\\[1mm]
मु.उ. & मुण्डक उपनिषद्\\[1mm]
मे.को.धा.व. & मेदिनीकोष धान्तवर्ग\\[1mm]
र.वं. & रघुवंश \\[1mm]
रा.र.स्तो. & रामरक्षास्तोत्र\\[1mm]
वा.रा. & वाल्मीकीय रामायण \\[1mm]
वि.प. & विनयपत्रिका \\[1mm]
वि.पु. & विष्णुपुराण\\[1mm]
वै.म.भा. & वैष्णवमताब्जभास्कर\\[1mm]
स्क.पु.ब्र.ख.ध.मा. & स्कन्दपुराण ब्रह्मखण्ड धर्मारण्यमाहात्म्य \\[1mm]
स्क.पु.रे.ख.स.क. & स्कन्दपुराण रेवाखण्ड सत्यनारायणकथा\\[1mm]
ह.बा. & हनुमान बाहुक \\[1mm]
हि. & हितोपदेश\\[1mm]
हि.प्र. & हितोपदेश प्रस्तावना\\[1mm]
